{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-06 proposal/410.tex
several small changes

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.96\textwidth]{p2-p3-distribution.pdf}
	\end{center}
	\caption{Distribution of P2 (thrlib) and P3 (kernel) grades among students who did or didn't use Landslide.}
	\label{fig:grade-distribution}
\end{figure}

{\bf Future work.}
One evaluation question remains which I will answer in the thesis:
what is the accuracy of Landslide's automation heuristics (see previous section)?
In other words, were false-positive infinite loops or deadlocks ever reported
where Landslide failed to recognize an ad-hoc synchronization?
(I expect a near 100\% success rate,
having tuned the heuristics by hand on an (independent) set of P2 submissions already.)

>>>>

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.85\textwidth]{p2-p3-distribution.pdf}
	\end{center}
	\caption{Distribution of P2 (thrlib) and P3 (kernel) grades among students who did or didn't use Landslide.}
	\label{fig:grade-distribution}
\end{figure}

{\bf Future work.}
One evaluation question remains which I will answer in the thesis:
what is the accuracy of Landslide's automation heuristics?
In other words, were false-positive infinite loops or deadlocks ever reported
where Landslide failed to recognize an ad-hoc synchronization?
(I expect a near 100\% success rate,
having tuned the heuristics by hand on an (independent) set of P2 submissions already.)

### 2017-01-06 proposal/quicksand.tex
minor fixes
implementation deets
several small changes

\subsection{Pruning false-positive data-race candidates}
I have also proved a (somewhat less remarkable) theorem concerning the soundness of a new tactic for pruning certain types of false-positive data race candidates (under Limited HB).
A ``malloc-recycle'' false positive occurs when two threads seem to race on the same memory address, but only because the {\tt malloc}ed block containing that address was {\tt free}d and reallocated in between.
If the transitions of the two threads were reordered, the address collision would disappear and there would be no race.
The proof is available at \cite{quicksand-soundness}; the theorem statement is:

@@

\section{Evaluation}

@@

\begin{figure}[h]
	\begin{tabular}{cc}
		\begin{tabular}{p{0.48\textwidth}p{0.48\textwidth}}
			\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-v2.pdf}
		&
			\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-wallclock-v2.pdf}
		\\
			(a)
			Bugs found as a function of elapsed CPU time. After the break-even point at
			\textasciitilde{}200 seconds, Quicksand outperforms all control experiments.
		&
			(b)
			Bugs found by elapsed wall-clock time.
			This presentation emphasizes that the ``break-even'' point in (a)
			is just an artifact of parallelization start-up overhead.
			Quicksand is parallelized tenfold; the vertical line indicates its 1 hour limit.
		\\
			\includegraphics[width=0.48\textwidth]{totalverifs-v2.pdf}
		&
			\includegraphics[width=0.48\textwidth]{nondets.pdf}
		\\
			(c)
			Total verifications provided as a function of CPU time.
			The lines for SSS-MC-ICB and SSS-MC-DPOR are artificially penalized to exclude tests with data races,
			as preempting on sync APIs alone is not sufficient to verify those.
			SSS-MC-Shared-Mem, however, is not penalized thus;
			its failure here is due to the massive computational overhead from so many preemption points.
		&
			(d)
			Plot of how many data-race bugs were found using ``single-pass'' data-race candidates versus ``nondeterministic'' ones.
			With both Limited and Pure HB approaches, the MC's ability to find new data-race candidates in obscure thread interleavings led to more bugs found in all test cases.
			Between Limited and Pure HB, Pure HB is more reliant on this phenomenon, as Limited HB can often find more potential races on the first pass.
		\end{tabular}
	\end{tabular}
	\caption{Results.}
	\label{fig:graphs}
\end{figure}

>>>>

\subsection{Pruning False Positives} % data-race candidates}
I have also proved a (somewhat less remarkable) theorem concerning the soundness of a new tactic for pruning certain types of false-positive data race candidates (under Limited HB).
A ``malloc-recycle'' false positive occurs when two threads seem to race on the same memory address, but only because the {\tt malloc}ed block containing that address was {\tt free}d and reallocated in between.
If the transitions of the two threads were reordered, the address collision would disappear and there would be no race.
The proof is available at \cite{quicksand-soundness}; the theorem statement is:

@@

\section{Evaluation}
\label{sec:quicksand-eval}

@@

\begin{figure}[h]
	\begin{tabular}{cc}
		\begin{tabular}{p{0.48\textwidth}p{0.48\textwidth}}
			\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-v2.pdf}
		&
			\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-wallclock-v2.pdf}
		\\
			(a)
			Bugs found as a function of elapsed CPU time. After the break-even point at
			\textasciitilde{}200 seconds, Quicksand outperforms all control experiments.
		&
			(b)
			Bugs found by elapsed wall-clock time.
			This presentation emphasizes that the ``break-even'' point in (a)
			is just an artifact of parallelization start-up overhead.
			Quicksand is parallelized tenfold; the vertical line indicates its 1 hour limit.
		\\
			\includegraphics[width=0.48\textwidth]{totalverifs-v2.pdf}
		&
			\includegraphics[width=0.48\textwidth]{nondets.pdf}
		\\
			(c)
			Total verifications provided as a function of CPU time.
			The lines for SSS-MC-ICB and SSS-MC-DPOR are artificially penalized to exclude tests with data races,
			as preempting on sync APIs alone is not sufficient to verify those.
			SSS-MC-Shared-Mem, however, is not penalized thus;
			its failure here is due to the massive computational overhead from so many preemption points.
		&
			(d)
			Plot of how many data-race bugs were found using ``single-pass'' data-race candidates versus ``nondeterministic'' ones.
			With both Limited and Pure HB approaches, the MC's ability to find new data-race candidates in obscure thread interleavings led to more bugs found in all test cases.
			Between Limited and Pure HB, Pure HB is more reliant on this phenomenon, as Limited HB can often find more potential races on the first pass.
		\end{tabular}
	\end{tabular}
	\caption{Many kernels died to bring us this information.}
	\label{fig:graphs}
\end{figure}
